\section{Twisting Lie-bialgebraic structures}
    \subsection{Twisted Manin triples and twisted topological Lie bialgebras} \label{subsection: twisted_manin_triples}
        For a recollection of basic facts about Manin triples, we refer the reader to subsection \ref{subsection: manin_triples}. We freely employ the notation scheme therein.

        Inspired by the theory of symmetric spaces, and following \cite{belliard_crampe_coideal_subalgebras_from_twisted_manin_triples}, we begin with the following definition.
        \begin{definition}[Twisted Manin triple] \label{def: twisted_manin_triples}
            Let:
                $$(\a, \a^+, \a^-)$$
            be a Manin triple (cf. definition \ref{def: manin_triples}) and consider a Lie algebra automorphism:
                $$\vartheta \in \Aut_{\LA}(\a)$$
            \begin{itemize}
                \item We say that $\vartheta$ is a \textbf{polar} (respectively, \textbf{anti-polar}) as a Manin triple automorphism if $\vartheta(\a^{\pm}) = \a^{\pm}$ (respectively, if $\vartheta(\a^{\pm}) = \a^{\mp}$).
                \item We say that $\vartheta$ \textbf{twists} the Manin triple above \textbf{(anti-)invariantly} if:
                    $$(\vartheta(x), y)_{\a} = \pm (x, \vartheta(y))_{\a}$$
                with the \say{$+$} sign corresponding to the invariant case, while the \say{$-$} sign corresponds to the anti-invariant case.
            \end{itemize}
        \end{definition}
        \begin{remark}
            Even when $\vartheta$ is a Lie algebra involution, our definition remains more general than \cite[Definition 2.1]{belliard_crampe_coideal_subalgebras_from_twisted_manin_triples}. Part of the reason for not insisting that the automorphism $\vartheta$ respects the polarisation of the Manin triple, i.e. not requiring that $\vartheta(\a^{\pm}) = \a^{\pm}$, is because we are interested also in examples of automorphisms such that $\vartheta(\a^{\pm}) = \a^{\mp}$. However, if we insist that $\vartheta$ respects the polarisation, then lemma \ref{lemma: twisted_manin_triples_and_twisted_topological_lie_bialgebras} in particular will only hold in a more restricted sense, which creates unnecessary inflexibility in our opinion.

            Interestingly, we will see through lemma \ref{lemma: manin_triple_twists_and_duality}, that an anti-invariant twist of a Manin triple $(\a, \a^+, \a^-)$ by an automorphism $\vartheta \in \Aut_{\LA}(\a)$ produces a topological Lie coideal subalgebra structure on the fixed-point subalgebra $\k := \a^{\vartheta}$ if and only if $\vartheta$ is a Lie algebra involution. That said, we are able to extend the results from \cite{belliard_crampe_coideal_subalgebras_from_twisted_manin_triples} to the case wherein $\vartheta$ is an \textit{anti-polar} involution that twists anti-invariantly. Note also that there are also involutions that twist \textit{invariantly}; see lemma \ref{lemma: manin_triple_twists_and_duality} for details.
        \end{remark}

        Recall that by duality, any Manin triple $(\a, \a^+, \a^-)$ gives rise to a topological Lie bialgebra structure $\delta: \a \to \a \hattensor \a$ by means of:
            $$\left( \delta(x), y \tensor z \right)_{\a \hattensor \a} = \left( x, [y, z] \right)_{\a} \quad, \quad x, y, z \in \a$$
        wherein $(\cdot, \cdot)_{\a \hattensor \a}$ is the factor-wise extension of the bilinear form $(\cdot, \cdot)_{\a}$ to $\a \hattensor \a$ (cf. equation \eqref{equation: lie_cobrackets_by_duality}). If $(\a, \a^+, \a^-)$ is twisted by a Lie algebra automorphism $\vartheta \in \Aut_{\LA}(\a)$, then:
            \begin{equation} \label{equation: twisting_lie_bialgebras_by_duality}
                \begin{aligned}
                    \pm \left( x, \vartheta([y, z]) \right)_{\a} & = \pm \left( x, [\vartheta(y), \vartheta(z)] \right)_{\a}
                    \\
                    & = \left( \vartheta(x), [y, z] \right)_{\a}
                    \\
                    & = \left( \delta( \vartheta(x), y \tensor z ) \right)_{\a \hattensor \a}
                \end{aligned}
            \end{equation}
        This prompts the following definition.
        \begin{definition}[Twisted topological Lie bialgebras] \label{def: twisted_topological_lie_bialgebras}
            Let $(\a, \delta)$ be a topological Lie bialgebra, and consider a Lie algebra automorphism\footnote{... which may not be a Lie bialgebra automorphism!}:
                $$\vartheta \in \Aut_{\LA}(\a)$$
            This is an \textbf{(anti-)invariant twist} of the Lie bialgebra structure $\delta$ if:
                $$\delta \circ \vartheta = \pm \vartheta^{\tensor 2} \circ \delta$$
            and like in definition \ref{def: twisted_manin_triples}, the \say{$+$} sign corresponding to the invariant case, while the \say{$-$} sign corresponds to the anti-invariant case.
        \end{definition}
        \begin{remark}
            An (anti-)invariant twist of a topological Lie bialgebra $(\a, \delta)$ by $\vartheta \in \Aut_{\LA}(\a)$ is the same as a topological Lie bialgebra (anti-)automorphism. However, it is more convenient to work with twists, especially in the anti-invariant case. This is because the codomain of an anti-automorphism of $\a$ is $\a^{\op}$, while the codomain of an automorphism of $\a$ is $\a$, so we are of the opinion that in order to avoid notational clutter, it is better to work with the notion of twists as in definition \ref{def: twisted_topological_lie_bialgebras}.
        \end{remark}
        For book-keeping purposes, let us record the following technical lemma.
        \begin{lemma}[Twisted Manin triples and twisted topological Lie bialgebras] \label{lemma: twisted_manin_triples_and_twisted_topological_lie_bialgebras}
            Let $(\a, \a^+, \a^-)$ be a Manin triple and let $\delta: \a \to \a \hattensor \a$ be the Lie bialgebra structure that it defines. Let $\vartheta \in \Aut_{\LA}(\a)$ be a Lie algebra automorphism. Then, $\vartheta$ twists the Manin triple $(\a, \a^+, \a^-)$ invariantly (respectively, anti-invariantly) if and only if it twists $\delta$ invariantly (respectively, anti-invariantly).
        \end{lemma}
            \begin{proof}
                This is clear by consideration of equation \eqref{equation: twisting_lie_bialgebras_by_duality} along with the correspondence \eqref{equation: manin_triple_lie_bialgebra_correspondence} between Manin triples and topological Lie bialgebras.
            \end{proof}

        The central question that we would like to address in this subsection is the following. An answer will be given by theorem \ref{theorem: twisted_lie_bialgebraic_structures}.
        \begin{question} \label{question: twisted_topological_lie_bialgebras}
            If $\vartheta \in \Aut_{\LA}(\a)$ is a twist of a general topological Lie bialgebra $(\a, \delta)$, then what sort of Lie-bialgebra structure:
                $$\delta^{\vartheta}$$
            will it induce onto the fixed-point subalgebra $\k := \a^{\vartheta}$ with ?
        \end{question}
        
        To provide an answer to question \ref{question: twisted_topological_lie_bialgebras}, we begin with an easy but useful lemma about the eigenspaces of a Lie algebra automorphism.
        \begin{lemma}[Symmetric space decompositions] \label{lemma: symmetric_space_decompositions}
            Let $\a$ be a Lie algebra being acted on by an automorphism $\vartheta \in \Aut_{\LA}(\a)$ and let:
                $$\a := \k \oplus \bigoplus_{ \mu \in \weight(\vartheta), \mu \not = 1 } \p_{\mu}$$
            be the eigenspace decomposition\footnote{See convention \ref{conv: endomorphisms} for an explanation of the notations.} induced by $\vartheta$; also, let $\p := \bigoplus_{ \mu \in \weight(\vartheta), \mu \not = 1 } \p_{\mu}$. Then, the following commutation relations hold for all $\mu, \nu \in \weight(\vartheta)$:
                \begin{equation} \label{equation: symmetric_space_relations}
                    [\p_{\mu}, \p_{\nu}] \subseteq \p_{\mu \nu}
                \end{equation}
            and consequently, we have that:
                $$[\k, \p] \subseteq \p \quad, \quad [\k, \k] \subseteq \k$$
        \end{lemma}
            \begin{proof}
                For $x \in \p_{\mu}$ and $y \in \p_{\nu}$, consider:
                    $$\vartheta( [x, y] ) = [ \vartheta(x), \vartheta(y) ] = [\mu \cdot x, \nu \cdot y] = \mu \nu \cdot [x, y]$$
                This tells us that $[x, y] \in \p_{\mu \nu}$, and so we have that $[\p_{\mu}, \p_{\nu}] \subseteq \p_{\mu \nu}$, as claimed. That $[\k, \p] \subseteq \p$ can be proven as follows:
                    $$[\k, \p] = \left[ \k, \bigoplus_{ \mu \in \weight(\vartheta), \mu \not = 1 } \p_{\mu} \right] = \sum_{ \mu \in \weight(\vartheta), \mu \not = 1 } [\k, \p_{\mu}] = \sum_{ \mu \in \weight(\vartheta), \mu \not = 1 } \p_{\mu} \subseteq \bigoplus_{ \mu \in \weight(\vartheta), \mu \not = 1 } \p_{\mu} =: \p$$
                while that $[\k, \k] \subseteq \k$ then follows from setting $\mu = \nu = 1$.
            \end{proof}
        \begin{remark}
            It is possible that for $\mu, \nu \in \weight(\vartheta)$, we may have $\mu \nu = 1$ even when $\mu, \nu \not = 1$. For instance, when $\vartheta$ is an involution, this occurs when $\mu = \nu = -1$. This means that in general, $\p$ is not a Lie subalgebra of $\a$, in contrast with $\k$ which is a Lie subalgebra (thanks to the relation $[\k, \k] \subseteq \k$).
        \end{remark}
        
        Next, let:
            $$(\a, \a^+, \a^-)$$
        be a Manin triple twisted - either anti-invariantly or invariantly - in the sense of definition \ref{def: twisted_manin_triples} by a Lie algebra automorphism $\vartheta \in \Aut_{\LA}(\a)$, and let us abbreviate:
            \begin{equation} \label{equation: polarised_symmetric_space_decompositions}
                \k^{\pm} := \k \cap \a^{\pm} \quad, \quad \p^{\pm} := \p \cap \a^{\pm}
            \end{equation}
        The relations \eqref{equation: symmetric_space_relations} then induces the following relations:
            \begin{equation} \label{equation: polarised_symmetric_space_relations}
                [\k^{\pm}, \p^{\pm}] \subseteq \p^{\pm} \quad, \quad [\k^{\pm}, \k^{\pm}] \subseteq \k^{\pm} 
            \end{equation}
        from which we infer in particular that while the subspaces $\k^{\pm}$ are Lie subalgebras of $\a^{\pm}$, the subspaces $\p^{\pm}$ are not.
        \begin{itemize}
            \item From the fact that $[\k^{\mp}, \p^{\mp}] \subseteq \p^{\mp}$, we see that $\p^{\mp}$ has the structure of a $\k^{\mp}$-module via the adjoint action. We regard this module structure as the linear map:
                \begin{equation} \label{equation: action_of_fixed_point_subalgebras_on_unfixed_points}
                    \rho^{\mp}: \k^{\mp} \tensor \p^{\mp} \to \p^{\mp}
                \end{equation}
            given by\footnote{For $\rho^-$, the additional minus sign is necessary for keeping track of the fact that $\a- \cong (\a^+)^{*, \op, \cop}$ as Lie bialgebras.}:
                $$\rho^{\mp}(x \tensor y) := \mp [x, y]_{\a^{\mp}} \quad, \quad x \in \k^{\mp}, y \in \p^{\mp}$$
            Dualising the map \eqref{equation: action_of_fixed_point_subalgebras_on_unfixed_points} then yields a linear map $(\rho^{\mp})^*: (\p^{\mp})^* \to (\k^{\mp} \tensor \p^{\mp})^*$. Should we have that $(\k^{\mp})^* \hattensor (\p^{\mp})^* \subseteq (\k^{\mp} \tensor \p^{\mp})^*$, then $\rho^*$ would extend to a topological $(\a^{\mp})^*$-comodule structure on $(\p^{\mp})^*$, which we (abusively) denote by the same symbol:
                $$(\rho^{\mp})^*: (\p^{\mp})^* \to (\a^{\mp})^* \hattensor (\p^{\mp})^*$$
            \item Likewise, by dualising the Lie bracket on $\k^{\mp}$, one obtains a linear map:
                \begin{equation} \label{equation: dual_brackets_on_fixed_point_subalgebras}
                    [\cdot, \cdot]_{\k^{\mp}}^*: (\k^{\mp})^* \to (\k^{\mp} \tensor \k^{\mp})^*
                \end{equation}
            which would define a topological Lie bialgebra structure on $(\k^{\mp})^*$ should we have that $(\k^{\mp})^* \hattensor (\k^{\mp})^* \subseteq (\k^{\mp} \tensor \k^{\mp})^*$.
        \end{itemize}
        To those ends, recall from definition \ref{def: manin_triples} that for Manin triples $(\a, \a^+, \a^-)$, we assume that the dual brackets $\delta^{\pm} := [\cdot, \cdot]_{\a^{\mp}}^*: (\a^{\mp})^* \to (\a^{\mp} \tensor \a^{\mp})^*$ factor through $(\a^{\mp})^* \hattensor (\a^{\mp})^*$. We see thus that equation \eqref{equation: action_of_fixed_point_subalgebras_on_unfixed_points} defines a topological $(\a^{\mp})^*$-comodule structure on $(\p^{\mp})^*$:
            \begin{equation} \label{equation: coactions_on_dual_of_unfixed_points}
                (\rho^{\mp})^*: (\p^{\mp})^* \to (\a^{\mp})^* \hattensor (\p^{\mp})^*
            \end{equation}
        while equation \eqref{equation: dual_brackets_on_fixed_point_subalgebras} yields us a topological Lie bialgebra structure on $(\k^{\mp})^*$:
            \begin{equation} \label{equation: cobrackets_on_fixed_points}
                [\cdot, \cdot]_{\k^{\mp}}^*: (\k^{\mp})^* \to (\k^{\mp})^* \hattensor (\k^{\mp})^*
            \end{equation}
        \begin{remark}
            We would like to note that $[\cdot, \cdot]_{\k^{\mp}}^*$ is usually not a Lie sub-bialgebra structure of $\delta^{\pm} := [\cdot, \cdot]_{\a^{\mp}}^*$, which is a map $(\k^{\mp})^* \to (\k^{\mp})^* \hattensor (\k^{\mp})^* + (\p^{\mp})^* \hattensor (\p^{\mp})^*$ instead.
        \end{remark}
        
        Our next task is to compute the dual spaces $(\p^{\mp})^*$ and $(\k^{\mp})^*$, and we shall see that this depends on whether the Manin triple being considered is twisted anti-invariantly or invariantly.
        
        \begin{lemma}[Manin triple twists and duality] \label{lemma: manin_triple_twists_and_duality}
            Let $(\a, \a^+, \a^-)$ be a Manin triple which is twisted in the sense of definition \ref{def: twisted_manin_triples} by a Lie algebra automorphism $\vartheta \in \Aut_{\LA}(\a)$, and let $\k^{\pm}, \p^{\pm}$ be as in \eqref{equation: polarised_symmetric_space_decompositions}. Then, via the isomorphisms \eqref{equation: manin_triple_currying}, we can make the following identifications of $(\p^{\mp})^*$ and $(\k^{\mp})^*$.
            \begin{enumerate}
                \item $\vartheta$ twists $(\a, \a^+, \a^-)$ anti-invariantly if and only if:
                    \begin{equation} \label{equation: anti_invariant_twist_duality}
                        (\p^{\mp})^* \cong \bigoplus_{ \mu \in \weight(\vartheta), \mu \not = -1 } \p_{\mu}^{\pm} \quad, \quad (\k^{\mp})^* \cong \p_{-1}^{\pm}
                    \end{equation}
                \item $\vartheta$ twists $(\a, \a^+, \a^-)$ invariantly if and only if:
                    \begin{equation} \label{equation: invariant_twist_duality}
                        (\p^{\mp})^* \cong \p^{\pm} \quad, \quad (\k^{\mp})^* \cong \k^{\pm}
                    \end{equation}
            \end{enumerate}
            with both cases holding regardless of whether $\vartheta$ is polar or anti-polar.
        \end{lemma}
        \begin{remark} \label{remark: manin_triple_twists_via_currying}
            Let us take a slight detour and discuss a re-interpretation of definition \ref{def: twisted_manin_triples} that will be useful for the proof of lemma \ref{lemma: manin_triple_twists_and_duality}.
        
            Recall that the data defining a Manin triple $(\a, \a^+, \a^-)$ (cf. definition \ref{def: manin_triples}) consists in particular of isomorphisms of vector spaces\footnote{Recall from definition \ref{def: manin_triples} that the dual spaces $(\a^{\mp})^*$ are equipped with the weak topology, and $\a = \a^+ \oplus \a^-$ is equipped with the product topology.}:
                $$\beta^{\pm}: \a^{\pm} \xrightarrow[]{\cong} (\a^{\mp})^*$$
            given by:
                $$\beta^{\pm}(x) := (x, \cdot)_{\a} \quad, \quad x \in \a^{\pm}$$
            (cf. equation \eqref{equation: manin_triple_currying}). Using these isomorphisms, we can rephrase definition \ref{def: twisted_manin_triples} as follows: a polar Lie algebra automorphism $\vartheta \in \Aut_{\LA}(\a)$ is a twist of a Manin triple $(\a, \a^+, \a^-)$ if and only if either of the following diagrams in the category of topological vector spaces commutes:
                \begin{equation} \label{diagram: manin_triple_polar_twist_currying}
                    \begin{tikzcd}
                    	{\a^+} & {\a^+} \\
                    	{(\a^-)^*} & {(\a^-)^*}
                    	\arrow["\vartheta|_{\a^+}", from=1-1, to=1-2]
                    	\arrow["{\beta^+}"', from=1-1, to=2-1]
                    	\arrow["{\beta^+}", from=1-2, to=2-2]
                    	\arrow["{\pm \vartheta|_{\a^-}^*}", from=2-1, to=2-2]
                    \end{tikzcd}
                \end{equation}
            with \say{$-\vartheta^*$} corresponding to the anti-invariant case while \say{$\vartheta^*$} corresponding to the invariant case.

            Twisting by an anti-polar automorphism has a completely analogous re-interpretation in terms of the following commutative diagram:
                \begin{equation} \label{diagram: manin_triple_anti_polar_twist_currying}
                    \begin{tikzcd}
                    	{\a^+} & {\a^-} \\
                    	{(\a^-)^*} & {(\a^+)^*}
                    	\arrow["\vartheta|_{\a^+}", from=1-1, to=1-2]
                    	\arrow["{\beta^+}"', from=1-1, to=2-1]
                    	\arrow["{\beta^-}", from=1-2, to=2-2]
                    	\arrow["{\pm \vartheta|_{\a^+}^*}", from=2-1, to=2-2]
                    \end{tikzcd}
                \end{equation}
        \end{remark}
            \begin{proof}[Proof of lemma \ref{lemma: manin_triple_twists_and_duality}]
                The polar and anti-polar cases are completely analogous to one another, so let us discuss only the former.

                Through the fact that $\k^{\pm} = \ker(\vartheta|_{\a^{\pm}} - 1)$ and through diagram \eqref{diagram: manin_triple_polar_twist_currying}, we see that the following diagram commutes:
                    \begin{equation} \label{diagram: manin_triple_twists_and_duality}
                        \begin{tikzcd}
                        	0 & {\k^+} & {\a^+} & {\a^+} & {\p^+} & 0 \\
                        	0 & {\beta^+(\k^+)} & {(\a^-)^*} & {(\a^-)^*} & {\beta^+(\p^+)} & 0
                        	\arrow[from=1-1, to=1-2]
                        	\arrow["\ker", from=1-2, to=1-3]
                        	\arrow["{\beta^+}"', dashed, from=1-2, to=2-2]
                        	\arrow["{\vartheta|_{\a^+} - 1}", from=1-3, to=1-4]
                        	\arrow["{\beta^+}"', from=1-3, to=2-3]
                        	\arrow["\coker", from=1-4, to=1-5]
                        	\arrow["{\beta^+}", from=1-4, to=2-4]
                        	\arrow[from=1-5, to=1-6]
                        	\arrow["{\beta^+}", dashed, from=1-5, to=2-5]
                        	\arrow[from=2-1, to=2-2]
                        	\arrow[from=2-2, to=2-3]
                        	\arrow["{\pm \vartheta|_{\a^-}^* - 1}", from=2-3, to=2-4]
                        	\arrow[from=2-4, to=2-5]
                        	\arrow[from=2-5, to=2-6]
                        \end{tikzcd}
                    \end{equation}
                Since the vertical arrows are isomorphisms (see remark \ref{remark: manin_triple_twists_via_currying} for more details), the bottom row of diagram \eqref{diagram: manin_triple_twists_and_duality} is also an exact sequence, and we see thus that:
                    $$
                        \begin{gathered}
                            \beta^+(\k^+) \cong \ker(\pm \vartheta|_{\a^-}^* - 1)
                            \\
                            \beta^+(\p^+) \cong \coker(\pm \vartheta|_{\a^-}^* - 1)
                        \end{gathered}
                    $$
                Using the setup above, let us now prove the stated claims.
                \begin{enumerate}
                    \item Assume first of all that $\vartheta$ twists anti-invariantly. In this case, the middle arrow in the bottom row in diagram \eqref{diagram: manin_triple_twists_and_duality} is:
                        $$-\vartheta|_{\a^-}^* - 1 = -( \vartheta|_{\a^-}^* + 1 )$$
                    (cf. diagram \eqref{diagram: manin_triple_polar_twist_currying}). From this, we see that:
                        $$\beta^+(\k^+) \cong \ker(-\vartheta|_{\a^-}^* - 1) = \ker(\vartheta|_{\a^-}^* + 1) = \ker(\vartheta|_{\a^-} + 1)^* = (\p_{-1}^-)^*$$
                    As $\beta^+: \a^+ \to (\a^-)^*$ is an isomorphism, we have $\beta^+(\k^+) \oplus \beta^+(\p^+) = \beta^+(\k^+ \oplus \p^+) = \beta^+(\a^+)$, and hence:
                        $$\beta^+(\p^+) = \frac{\beta^+(\a^+)}{\beta^+(\k^+)} = \beta^+\left( \bigoplus_{ \mu \in \weight(\vartheta), \mu \not = -1 } \p_{\mu}^+ \right) \cong \left( \bigoplus_{ \mu \in \weight(\vartheta), \mu \not = -1 } \p_{\mu}^- \right)^*$$

                    Conversely, assume that $\beta^+(\k^+) = (\p^-_{-1})^*$ and $\beta^+(\p^+) = \left( \bigoplus_{ \mu \in \weight(\vartheta), \mu \not = -1 } \p_{\mu}^- \right)^*$. This means that $\beta^+(\k^+) = \ker(-\vartheta|_{\a^-}^* - 1) = \ker( \vartheta|_{\a^-}^* + 1 )$, and hence the middle arrow in the bottom row in diagram \eqref{diagram: manin_triple_twists_and_duality} to be:
                        $$-\vartheta|_{\a^-}^* - 1 = -( \vartheta|_{\a^-}^* + 1 )$$
                    According to diagram \eqref{equation: manin_triple_currying}, $\vartheta$ must then twist the Manin triple $(\a, \a^+, \a^-)$ anti-invariantly.
                    \item Now, assume that $\vartheta$ twists invariantly. Then, because $(\vartheta|_{\a^+} - 1)^* = \vartheta|_{\a^+}^* - 1$, the lower row in diagram \eqref{diagram: manin_triple_twists_and_duality} coincides with the following diagram:
                        \begin{equation}
                            \begin{tikzcd}
                            	0 & {(\p^-)^*} & {(\a^-)^*} & {(\a^-)^*} & {(\p^-)^*} & 0
                            	\arrow[from=1-1, to=1-2]
                            	\arrow["\ker", from=1-2, to=1-3]
                            	\arrow["{(\vartheta|_{\a^-} - 1)^*}", from=1-3, to=1-4]
                            	\arrow["\coker", from=1-4, to=1-5]
                            	\arrow[from=1-5, to=1-6]
                            \end{tikzcd}
                        \end{equation}
                    This is the exact sequence obtained by dualising the top row in diagram \eqref{diagram: manin_triple_twists_and_duality}, i.e. by applying the functor $(-)^* := \Hom(-, \bbk)$ to it, and then appealing to the fact that this functor is exact. Putting everything together, we see that:
                        $$
                            \begin{gathered}
                                \beta^+(\k^+) \cong \ker(\vartheta|_{\a^-}^* - 1) \cong (\k^-)^*
                                \\
                                \beta^+(\p^+) \cong \coker(\vartheta|_{\a^-}^* - 1) \cong (\p^-)^*
                            \end{gathered}
                        $$
                        
                    Conversely, assume that $\beta^+(\p^+) = (\p^-)^*$ and $\beta^+(\k^+) = (\k^-)^*$. Since $(\k^-)^* = \ker(\vartheta|_{\a^+}^* - 1)^*$, this forces the middle arrow in the bottom row in diagram \eqref{diagram: manin_triple_twists_and_duality} to be:
                        $$\vartheta|_{\a^-}^* - 1$$
                    According to diagram \eqref{equation: manin_triple_currying}, $\vartheta$ must then twist the Manin triple $(\a, \a^+, \a^-)$ invariantly.
                \end{enumerate}
            \end{proof}
        \begin{remark}
            Interestingly, the duality patterns for both the polar and anti-polar cases turn out to be the same. Therefore, there are no \textit{abstract} qualitative differences between these two scenarios. However, the fixed-point subalgebras can behave quite differently between the two cases.
        \end{remark}
        
        Combining lemma \ref{lemma: manin_triple_twists_and_duality} with the observations leading up to it, we obtain the following rough classification of Lie-bialgebraic twists in the sense of definition \ref{def: twisted_topological_lie_bialgebras}.

        \todo[inline]{I was not expecting this, but it seems that an anti-invariant twist can only be done by an involution, if we are to obtain a coideal subalgebra structure on the fixed-point subalgebra out of this twisting procedure. One can get coideal subalgebras from non-involutive automorphisms, as in \cite{schrader_integrable_systems_from_classical_reflection_equations}, but these do not originate from the notion of Manin triple/Lie bialgebra twists by Belliard-Crampé from \cite{belliard_crampe_coideal_subalgebras_from_twisted_manin_triples} (the same notion used in \cite{belliard_regelskis_J_presentation_for_twisted_yangians} and \cite{guay_regelskis_twisted_yangians_for_symmetric_pairs_of_types_BCD}). I'm not yet sure what the correct generalisation of anti-invariant twists to non-involutive automorphisms ought to be. Perhaps, for a finite-order automorphism of order $N$, one can replace the $-1$ factor by an $N^{th}$ root of unity; when $N = 2$, we regard the $-1$ factor as a $2^{nd}$ root of unity.}
        
        \begin{theorem}[Twisted Lie bialgebraic structures] \label{theorem: twisted_lie_bialgebraic_structures}
            We keep the notations from lemma \ref{lemma: manin_triple_twists_and_duality}, and let:
                $$\delta^{\pm}: \a^{\pm} \to \a^{\pm} \hattensor \a^{\pm}$$
            be the topological Lie algebra structures defined by the Manin triple $(\a, \a^+, \a^-)$ via equation \eqref{equation: lie_cobrackets_by_duality}. Also, for a Lie algebra automorphism:
                $$\vartheta \in \Aut_{\LA}(\a)$$
            let us write:
                \begin{equation} \label{equation: twisted_lie_cobrackets}
                    (\delta^{\pm})^{\vartheta} :=
                    \begin{cases}
                        \delta^{\pm} \circ \vartheta|_{\a^{\pm}} & \text{if and only if $\vartheta$ twists $(\a^{\pm}, \delta^{\pm})$ anti-invariantly}
                        \\
                        [\cdot, \cdot]_{\k^{\mp}}^* & \text{if and only if $\vartheta$ twists $(\a^{\pm}, \delta^{\pm})$ invariantly}
                    \end{cases}
                \end{equation}
            \begin{enumerate}
                \item $(\k^{\pm}, (\delta^{\pm})^{\vartheta})$ are topological Lie coideal subalgebras of $(\a^{\pm}, \delta^{\pm})$ if and only if $\vartheta \in \Aut_{\LA}(\a)$ is an involution that twists the topological Lie bialgebras $(\a^{\pm}, \delta^{\pm})$ anti-invariantly.
                \item $(\k^{\pm}, (\delta^{\pm})^{\vartheta})$ are new topological Lie bialgebras if and only if $\vartheta \in \Aut_{\LA}(\a)$ twists the topological Lie bialgebras $(\a^{\pm}, \delta^{\pm})$ invariantly. In this case, $\vartheta$ needs not be an involution.
            \end{enumerate}
        \end{theorem}
            \begin{proof}
                \begin{enumerate}
                    \item Combine lemma \ref{lemma: manin_triple_twists_and_duality} with equation \eqref{equation: coactions_on_dual_of_unfixed_points}.
                    \item Combine lemma \ref{lemma: manin_triple_twists_and_duality} with equation \eqref{equation: cobrackets_on_fixed_points}.
                \end{enumerate}
            \end{proof}

        Finally, we note that the operation of twisting is compatible with the construction of classical doubles in the sense of Drinfeld. The precise statement can be phrased as a corollary to theorem \ref{theorem: twisted_lie_bialgebraic_structures} as follows.
        \begin{corollary}[Compatibility between twists and classical doubles] \label{coro: twisting_classical_doubles}
            Let us keep the notations from theorem \ref{theorem: twisted_lie_bialgebraic_structures}. Also, let:
                \begin{equation} \label{equation: twisting_classical_doubles}
                    \delta^{\vartheta} := (\delta^+)^{\delta} \oplus (-\delta^-)^{\vartheta}
                \end{equation}
            \begin{enumerate}
                \item $(\k, \delta^{\vartheta})$ is a topological Lie coideal subalgebra of $(\a, \delta)$ if and only if $\vartheta \in \Aut_{\LA}(\a)$ is an involution that twists the topological Lie bialgebra $(\a, \delta)$ anti-invariantly.
                \item $(\k, \delta^{\vartheta})$ is another topological Lie bialgebra if and only if $\vartheta \in \Aut_{\LA}(\a)$ twists the topological Lie bialgebra $(\a, \delta)$ invariantly. In this case, $\vartheta$ needs not be an involution.
                
                Furthermore, we have:
                    $$\k \cong \Dr(\k^+) \cong \Dr(\k^-)^{\op, \cop}$$
                which then implies via the correspondence \eqref{equation: manin_triple_lie_bialgebra_correspondence}, that the following is a Manin triple:
                    $$(\k, \k^+, \k^-)$$
            \end{enumerate}
        \end{corollary}
            \begin{proof}
                \begin{enumerate}
                    \item By lemma \ref{lemma: manin_triple_twists_and_duality}, what follows is true if and only if $\vartheta \in \Aut_{\LA}(\a)$ is an involution that twists $(\a, \delta)$ anti-invariantly.
                    
                    Taking the direct sum of the two maps \eqref{equation: coactions_on_dual_of_unfixed_points} yields us a topological $\a^*$-comodule structure:
                        $$\rho^*: \p^* \to \a^* \hattensor \p^*$$
                    (topologically dual to the action $\rho: \k \hattensor \p \to \p$ given by $x \tensor y \mapsto [x, y]_{\a}$), and this comodule structure is to fit into the following commutative diagram, in which the unlabelled arrows are the canonical ones:
                        $$
                            \begin{tikzcd}
                            	{\left( (\a^-)^* \hattensor (\p^-)^* \right) \oplus \left( (\a^+)^{*, \op, \cop} \hattensor (\p^+)^* \right)} && {\left( (\a^-)^* \hattensor (\p^-)^* \right) \oplus \left( (\p^+)^* \hattensor (\a^+)^* \right)} \\
                            	{(\p^-)^* \oplus (\p^+)^*} && {\left( \a^* \hattensor (\p^-)^* \right) \oplus \left( (\p^+)^* \hattensor \a^* \right)} \\
                            	{(\p^- \oplus \p^+)^*} && {\left( \a^* \hattensor (\p^- \oplus \p^+)^* \right) \oplus \left( (\p^- \oplus \p^+)^* \hattensor \a^* \right)} \\
                            	{\p^*} && {\left( \a^* \hattensor \p^* \right) \oplus \left( \p^* \hattensor \a^* \right)}
                            	\arrow["\cong", from=1-1, to=1-3]
                            	\arrow[hook, from=1-3, to=2-3]
                            	\arrow["{(\rho^-)^* \oplus (\rho^+)^*}", from=2-1, to=1-1]
                            	\arrow["\cong"', from=2-1, to=3-1]
                            	\arrow[hook, from=2-3, to=3-3]
                            	\arrow["\cong"', from=3-1, to=4-1]
                            	\arrow["\cong", from=3-3, to=4-3]
                            	\arrow["{\rho^*}", from=4-1, to=4-3]
                            \end{tikzcd}
                        $$
                    Note also, that we have made use of the fact that there is an isomorphism of topological Lie bialgebras:
                        $$\a \cong \Dr(\a^+) := \a^+ \oplus ( \a^+ )^{*, \op, \cop} \cong \a^+ \oplus (\a^-)^{\op, \cop}$$
                    (see remark \ref{remark: embeddings_into_classical_doubles} for more details). Then, by identifying $\a^* \cong \a$ as topological Lie bialgebras and $(\p^{\mp})^* \cong \k^{\pm}$ (using lemma \ref{lemma: manin_triple_twists_and_duality}) and hence $\p^* \cong \k$ (since $\k = \k^+ \oplus \k^-$ and $\p = \p^+ \oplus \p^-$), we will get a topological $\a$-comodule structure:
                        $$\rho^*: \k \to \a \hattensor \k$$
                    Lastly, because $\k$ is a Lie subalgebra of $\a$ (cf. equation \eqref{equation: symmetric_space_relations}), $\rho^*$ is actually a coideal subalgebra structure coinciding with $\delta^{\vartheta}$.
                    \item Reasoning as above, we can show that $(\k, \delta^{\vartheta})$ is a topological Lie bialgebra if and only if $\vartheta \in \Aut_{\LA}(\a)$ twists $(\a, \delta)$ invariantly.
                    
                    Then, to prove that:
                        $$\k \cong \Dr(\k^+) \cong \Dr(\k^-)^{\op, \cop}$$
                    we need merely recall that there is an isomorphism of topological Lie bialgebras:
                        $$\a \cong \Dr(\a^+) := \a^+ \oplus ( \a^+ )^{*, \op, \cop} \cong \a^+ \oplus (\a^-)^{\op, \cop}$$
                    (again, see remark \ref{remark: embeddings_into_classical_doubles} for more details), and then that $\k^{\pm}$, respectively, are Lie subalgebras of $\a^{\pm}$ (this follows from the relations \eqref{equation: symmetric_space_relations}).
                \end{enumerate}
            \end{proof}
            
        \begin{remark}[Pseudo-fixed-point topological Lie coideal subalgebras ?] \label{remark: notations_for_twisted_lie_bialgebraic_structures}
            Later on, we would also like to investigate the evaluation of the twisted structure $\delta^{\vartheta}$ on Lie subalgebras of $\a$ which, despite being defined by the automorphism $\vartheta$, are not fixed-point subalgebras. Instead, we may consider the values of $\delta^{\vartheta}$ on the so-called \say{pseudo-fixed-point subalgebras}, which have been studied in \cite{regelskis_vlaar_finite_QSPs_via_generalised_satake_diagrams} and \cite{regelskis_vlaar_kac_moody_pseudo_symmetric_pairs} as combinatorially motivated generalisations of the notion of \say{quantum symmetric pairs} (also called \say{$\i$quantum groups}) that had been previously studied by Letzter, Kolb, Stokman, Noumi, Sugitani, and many others (see e.g. \cite{letzter_coideal_subalgebras_and_QSPs} and \cite{kolb_kac_moody_QSPs}). Note also that such generalisations have only been made within the Kac-Moody setting, and to our knowledge, no Yangian or elliptic analogues of the notion of pseudo-fixed-point subalgebras have ever been studied.
        \end{remark}
        
        In conclusion, there are two possibilities when a Lie bialgebra $(\a, \delta)$ is twisted in the sense of definition \ref{def: twisted_topological_lie_bialgebras}. Namely, either the fixed-point subalgebra $\k \subseteq \a$ gives rise to a topological Lie coideal subalgebra:
            $$\delta^{\vartheta}: \k \to \a \hattensor \k + \k \hattensor \a$$
        if and only if the twist is anti-invariant and by an involution, or another Lie bialgebra structure:
            $$\delta^{\vartheta}: \k \to \k \hattensor \k$$
        if and only if the twist is invariant (by any automorphism). Our next order of business shall be to explicitly compute the expressions:
            $$\delta^{\vartheta}(x) \quad, \quad x \in \k$$
        Only coboundary topological Lie bialgebras (and in particular, the quasi-triangular ones) are of relevance to questions surrounding quantisation, so henceforth, let us focus on twists of such topological Lie bialgebras.

    \subsection{Twisting topological Lie comodules}
        Suppose that $(\a, \a^+, \a^-)$ is a Manin triple defining a topological Lie bialgebra structure $\delta^+: \a^+ \to \a^+ \hattensor \a^+$ via \eqref{equation: lie_cobrackets_by_duality}, and that $V$ is a topological left-$\a^+$-comodule\footnote{What follows works identically for right-comodules, so it suffices to only consider left-modules.}, determined by:
            $$\pi^+: V \to \a^+ \hattensor V$$
        Suppose also, that there is an automorphism $\sigma \in \Aut_{\LA}(\a)$ that twists the Manin triple $(\a, \a^+, \a^-)$ in the sense of definition \ref{def: twisted_manin_triples}.
        
        By theorem \ref{theorem: twisted_lie_bialgebraic_structures}, we know that if $\sigma$ twists anti-invariantly, then the fixed-point subalgebra $(\a^+)^{\sigma} = \a^+ \cap \a^{\sigma}$ will gain the structure of a topological Lie coideal subalgebra of $\a^+$ via the coaction \eqref{equation: coactions_on_dual_of_unfixed_points}. In that case, it would not even make sense to ask if $V$ would be a topological $(\a^+)^{\sigma}$-comodule, so let us focus on $\sigma$ twisting \textit{invariantly}. By theorem \ref{theorem: twisted_lie_bialgebraic_structures} again, we know that $((\a^+)^{\sigma}, (\delta^+)^{\sigma})$ (with notations as in \textit{loc. cit.}) is another topological Lie bialgebra in that case, and thus we can meaningfully inquire into whether or not $V$ will then be a topological $(\a^+)^{\sigma}$-comodule. This is equivalent to the following question.
        \begin{question} \label{question: invariant_twists_of_topological_lie_comodules}
            Under which conditions does the following corestriction exist:
                $$
                    \begin{tikzcd}
                    	& {(\a^+)^{\sigma} \hattensor V} \\
                    	V & {\a^+ \hattensor V}
                    	\arrow[from=1-2, to=2-2]
                    	\arrow["{}", dashed, from=2-1, to=1-2]
                    	\arrow["{\pi^+}", from=2-1, to=2-2]
                    \end{tikzcd}
                $$
            In other words, when do we have $\im \pi^+ \subseteq (\a^+)^{\sigma} \hattensor V$ ?
        \end{question}

        Assume now that $V$ is also acted on by the cyclic group $\<\sigma\>$ and that the coaction $\pi^+$ is moreover a $\<\sigma\>$-module homomorphism. Assume also, that there is an eigenspace decomposition $V = \bigoplus_{\mu \in \Pi(\sigma, V)} V_{\mu}$. Group cohomology supplies us with an induced map:
            $$(\pi^+)^{\sigma} := H^0_{\Grp}( \<\sigma\>, \pi^+ ): H^0_{\Grp}( \<\sigma\>, V ) \to H^0_{\Grp}( \<\sigma\>, \a^+ \hattensor V )$$
        and let us recall also that the zeroth cohomology functor is nothing but the fixed-point functor, due to the fact that there are natural isomorphisms:
            $$H^0_{\Grp}( \<\sigma\>, - ) \cong \Hom_{\bbk\<\sigma\>}(\bbk, -) \cong (-)^{\sigma}$$
        This means that we have a map:
            $$(\pi^+)^{\sigma}: V^{\sigma} \to (\a^+ \hattensor V)^{\sigma}$$
        Moreover, because we have eigenspace decompositions $\a^+ = \bigoplus_{\lambda \in \Pi(\sigma, \a^+)} \a^+_{\lambda}$ and $V = \bigoplus_{\mu \in \Pi(\sigma, V)} V_{\mu}$ wherein the eigenvalue $1$ corresponds to the fixed-point subspace, we have that:
            $$
                \begin{aligned}
                    \a^+ \hattensor V & \cong \left( \bigoplus_{\lambda \in \Pi(\sigma, \a^+)} \a^+_{\lambda} \right) \hattensor \left( \bigoplus_{\mu \in \Pi(\sigma, V)} V_{\mu} \right)
                    \\
                    & \cong (\a^+)^{\sigma} \hattensor V^{\sigma} \oplus \bigoplus_{ \substack{ \lambda \in \Pi(\sigma, \a^+), \mu \in \Pi(\sigma, V) \\ \lambda, \mu \not = 1 } } \a^+_{\lambda} \hattensor V_{\mu}
                \end{aligned}
            $$
        From this, we see that:
            $$(\a^+ \hattensor V)^{\sigma} \cong (\a^+)^{\sigma} \hattensor V^{\sigma}$$
        since the $\<\sigma\>$-action on $V$ extends to $\a^+ \hattensor V$ by means of\footnote{This is true more generally for tensor products of representations of any group.}:
            $$\sigma \cdot (x \tensor v) := (\sigma \cdot x) \tensor (\sigma \cdot v) \quad, \quad x \in \a^+, v \in V$$
        We see thus, that should the corestriction of $\pi^+$ as in question \ref{question: invariant_twists_of_topological_lie_comodules} exist, then it will fit into the following commutative diagram:
                $$
                    \begin{tikzcd}
                    	{V^{\sigma}} & {(\a^+)^{\sigma} \hattensor V^{\sigma}} \\
                    	V & {\a^+ \hattensor V}
                    	\arrow["{(\pi^+)^{\sigma}}", from=1-1, to=1-2]
                    	\arrow[from=1-1, to=2-1]
                    	\arrow[from=1-2, to=2-2]
                    	\arrow[dashed, from=2-1, to=1-2]
                    	\arrow["{\pi^+}", from=2-1, to=2-2]
                    \end{tikzcd}
                $$
        Therefore, if said corestriction exists, then $V^{\sigma}$ will automatically be an $(\a^+)^{\sigma}$-sub-comodule of $V$.
        \begin{remark}[Invariant twists of coideal subalgebras]
            For us, an answer to question \ref{question: invariant_twists_of_topological_lie_comodules} will be applicable to the following problem. Suppose that we have an automorphism $\vartheta \in \Aut_{\LA}(\a)$ twisting the Manin triple $(\a, \a^+, \a^-)$ \textit{anti-invariantly}, and let $\k^+ := \a^+ \cap \a^{\vartheta} = (\a^+)^{\vartheta}$. Theorem \ref{theorem: twisted_lie_bialgebraic_structures} tells us that $\k^+ \subset \a^+$ is a topological Lie coideal subalgebra via the coaction $(\rho^-)^*: \k^+ \to \a^+ \hattensor \k^+$ as in equation \eqref{equation: coactions_on_dual_of_unfixed_points}. Should $(\rho^-)^*$ admit a corestriction $\k^+ \to (\a^+)^{\sigma} \hattensor \k^+$, then $(\k^+)^{\sigma}$ will automatically be an $(\a^+)^{\sigma}$-sub-comodule of $\k^+$.

            This is useful, for instance, for producing examples of (quantum) symmetric pairs inside (quantum) Kac-Moody algebras of twisted affine types (in Kac's classification; see \cite[Chapter 4]{kac_infinite_dimensional_lie_algebras}) as invariant twists of those (quantum) symmetric pairs inside (quantum) Kac-Moody of untwisted affine types. This is because twisted affine Kac-Moody algebras arise as fixed-point subalgebras of untwisted affine Kac-Moody algebras under certain finite-order automorphisms (see \cite[Chapter 8]{kac_infinite_dimensional_lie_algebras}). We will study such examples in details in subsection \ref{subsection: twisted_affine_QSPS}.
        \end{remark}

        \todo[inline]{I think $V$ being a classical Yetter-Drinfeld module (cf. \cite[Subsection 2.8]{appel_laredo_2_categorical_etingof_kazhdan_quantisation}) is sufficient, since twisting is compatible with classical doubling (corollary \ref{coro: twisting_classical_doubles}). I'm not sure yet what a necessary condition on $V$ may be.}